---
title: "An Introduction to `debiased.subgroup`"
author: "Waverly Wei"
date: "Jan.2021"
output: 
  pdf_document:
    fig_caption: yes
    toc: yes
    toc_depth: 3
---
## Introduction
`debiased.subgroup` is a package that implements two bootstrap-assisted estimators: bootstrap-assisted desparsified Lasso and R-split. The two methods remove the subgroup selection bias and regularization bias indeced by high-dimensional covariates. 

## Installation
```{r, eval = FALSE,warning=FALSE,message=FALSE}
devtools::install_github("WaverlyWei/debiased.subgroup")
```

## Quick start
First we load the `debiased.subgroup` package:
```{r, warning=FALSE,message=FALSE}
library(debiased.subgroup)
```

We generate high-dimensional data with 2 subgroups of interest. We predefine a set of tuning parameters, denoted as $r$.
```{r,warning=FALSE,message=FALSE}
  library(MASS)
  library(glmnet)

  p <- 200 # number of confounders

  n <- 100 # sample size
  
  ngroups <- 2 # number of subgroups/treatments;
  
  s0 <- 4
  
  m <- ngroups
    
  Sigma <- matrix(0,p,p)
    
  for (i in 1:n){
      for(j in 1:p){
        Sigma[i,j] <- 0.5^(abs(i-j))
      }
    }
    
    # generate X 
    X <- mvrnorm( n = n, mu = rep(0,p), Sigma = Sigma )
    
    Z <- matrix(0,n,m)
    
    for(i in 1:n){
      for(j in 1:m){
        Z[i,j] <- rbinom(1,1,exp(X[i,2*j-1] + X[i,2*j])/(1+exp(X[i,2*j-1] + X[i,2*j])))
      }
    }
    
    
    # noise: heter/homo
    noise.y <- 1
    
    betas <- 1
    
    #index of the subgroups
    w.index <- seq(1, m, 1) 
    
    x <- cbind(Z,X)
    
    
    ## Model: Y = Z * beta + X * gamma + noise

    # Generate coefficients
    beta <- c(rep(0,m-1),betas) 
    
    gamma <- c(rep(1, s0), rep(0, p-s0)) 
    
    beta0 <- c(beta, gamma)
    
    # Generate noise 
    noise <- mvrnorm( n = 1, mu = rep(0,n), Sigma = diag(n) * noise.y )
    
    # Generate response Y 
    Y <- 0.5 + x %*% beta0 + noise
    
    ## parameters in the function
    r <- 1/(3*1:10)
    
```

## Bootstrap-calibrated Desparsified Lasso
Bootstrap iterations are recommended to be B = 200. Here we use B = 5 for demonstration purpose. 
```{r,cache=TRUE,warning=FALSE,message=FALSE}
desparse_res <- BSDesparseLasso(y = Y,
                                x = x, 
                                r = r, 
                                G = w.index,
                                B = 5)
```


### Result summary
The tuning parameter is selected through `cvDesparse`.
```{r,cache=TRUE,warning=FALSE,message=FALSE}
desparse_res$LowerBound
```

```{r,cache=TRUE,warning=FALSE,message=FALSE}
desparse_res$UpperBound
```

`betaMax` is the bias-reduced maximum beta estimate.
```{r,cache=TRUE,warning=FALSE,message=FALSE}
desparse_res$betaMax
```

`betaEst` contains the beta estimate for each subgroup.
```{r,cache=TRUE,warning=FALSE,message=FALSE}
desparse_res$betaEst
```

`op` is the cross-validated optimal tuning.
```{r,cache=TRUE,warning=FALSE,message=FALSE}
desparse_res$op
```


## Bootstrap-calibrated R-Split
Bootstrap iterations are recommended to be B = 200, BB = 1000. Here we use B = 5 and BB = 10 as demo. The tuning parameter is selected through `cvSplit`.

```{r,warning=FALSE,message=FALSE}
rsplit_res <- BSSplitLasso(y = Y,
                           x = x, 
                           r = r, 
                           G = w.index,
                           B = 5, BB = 10)
```

### Result summary
```{r,cache=TRUE,warning=FALSE,message=FALSE}
rsplit_res$LowerBound
```

```{r,cache=TRUE,warning=FALSE,message=FALSE}
rsplit_res$UpperBound
```

`betaMax` is the bias-reduced maximum beta estimate.
```{r,cache=TRUE,warning=FALSE,message=FALSE}
rsplit_res$betaMax
```

`betaEst` contains the beta estimate for each subgroup.
```{r,cache=TRUE,warning=FALSE,message=FALSE}
rsplit_res$betaEst
```

`modelSize` contains the R-split model size for each bootstrap iteration.
```{r,cache=TRUE,warning=FALSE,message=FALSE}
summary(rsplit_res$modelSize)
```

`op` is the cross-validated optimal tuning paramter
```{r,cache=TRUE,warning=FALSE,message=FALSE}
rsplit_res$op
```
